Profit Optimisation in Heterogeneous 2-link Parallel Games

### 2024-04-04 thesis/article.tex
Thesis: Adds corollary about max a_s and why higher a values are irrelevant

% Theorem structures.
\newtheorem{definition}{Definition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{example}{Example}[section]

@@

>>>>

% Theorem structures.
\newtheorem{definition}{Definition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{example}{Example}[section]
\newtheorem{corollary}{Corollary}[section]

@@

From the above lemma we can also observe the following

\begin{corollary}
	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$ and $x = (x_1, x_2)$ the optimal flow in the game without tolls, then $\as(t) \le \max\{\alpha(x_1), \alpha(x_2)\}$.
\end{corollary}

This corollary hints that all values of $\alpha$ above $\max\{x_1, x_2\}$ are irrelevant to the game.
This will become more obvious later when calculating best responses as those values will never be used.
[TODO: Maybe put this in its own Lemma and prove it?]
